\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-16 manuscript.Rnw
Add Jeroen's middle initial
Add health economic R packages to references

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Devin Incerti\\Genentech
   \And Jeroen Jansen\\University of California, San Francisco}
\Plainauthor{Devin Incerti, Jeroen Jansen}

@@

Despite their computational demands and foundations in statistics, health economic models have historically been developed with specialized commercial software (e.g., \proglang{TreeAge}) or more commonly with a spreadsheet (almost always Microsoft \proglang{Excel}). The limitations of such software relative to programming languages like \proglang{R} have been increasingly emphasized in the literature \citep{baio2017simple, incerti2019r, jalal2017overview}. It is therefore no surprise that a number of related \proglang{R} packages have recently been developed, such as \pkg{BCEA} \citep{baio2017bayesian}, \pkg{SAVI} \citep{strong2014estimating}, \pkg{survHE} \citep{baio2020survhe}, and \pkg{heemod} \citep{filipovic2017markov}. Still, of the available packages, only \pkg{heemod} provides a general purpose framework for developing simulation models and it is limited to Markov cohort models.

>>>>

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Devin Incerti\\Genentech
   \And Jeroen P Jansen\\University of California, San Francisco}
\Plainauthor{Devin Incerti, Jeroen Jansen}

@@

Despite their computational demands and foundations in statistics, health economic models have historically been developed with specialized commercial software (e.g., \proglang{TreeAge}) or more commonly with a spreadsheet (almost always Microsoft \proglang{Excel}). The limitations of such software relative to programming languages like \proglang{R} have been increasingly emphasized in the literature \citep{baio2017simple, incerti2019r, jalal2017overview}. It is therefore no surprise that a number of related \proglang{R} packages have recently been developed, such as \pkg{BCEA} \citep{baio2017bayesian}, \pkg{SAVI} \citep{strong2014estimating}, \pkg{dampack} \citep{alarid2018dampack}, \pkg{EVSI} \citep{heath2018efficient}, \pkg{survHE} \citep{baio2020survhe}, and \pkg{heemod} \citep{filipovic2017markov}. Still, of the available packages, only \pkg{heemod} provides a general purpose framework for developing simulation models and it is limited to Markov cohort models.
